DSSynth: An Automated Digital Controller Synthesis Tool for Physical Plants

### 2017-08-16 ase2017/paper.tex
fixed typos in section III
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

%---------------------------------------------------
\section{Synthesizing Digital Controllers with \tool}
%---------------------------------------------------

@@

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=0.47\textwidth]{synthesis-flow.pdf}
\caption{Phases of the Controller Synthesis}
\label{fig:synthesis-flow}
\end{figure}

In Step~1, the user selects the digital controller representation, which
can be a transfer function or a state-space model.  In Step~2, the
physical plant (in the form of Equation~(\ref{eq:transferfunction}) or
(\ref{eq:ss-example}), depending on representation) must be
given~\cite{astrom1997computer}.  Finally, in Step~3, the numerical
representation for the digital controller implementation must be set by the
user, i.e., the FWL format that defines the number of bits of the integer
and fractional parts as well as the dynamic range inputs.  The result of the
input given by the user is a specification of the physical plant.

@@

Our CEGIS engine is implemented as an integrated module within the C bounded
model checker (CBMC)~\cite{cbmc}.  CBMC transforms the ANSI-C representation
of our closed-loop control system model into its internal format.  We
instrument this IR for each synthesis or verification scenario accordingly,
and use CBMC as an oracle to answer our queries.  CBMC itself relies on an
underlying SAT or SMT solver to solve verification conditions.  We~model FWL
effects, time discretization and the presence of quantization noise
explicitly using CBMC's nondeterminism API (e.g., \texttt{nondet},
\texttt{CPROVER\_assume} intrinsic functions).  Our module is included in
CBMC~5.7 and is available for
download.\footnote{\url{https://github.com/diffblue/cbmc/archive/cbmc-5.7.zip}}
We further created a VirtualBox OVA image with our tool pre-installed,
including our MATLAB-generated benchmarks and benchmark shell script with
instructions to run all benchmarks and reproduce our
experiments.\footnote{\url{www.cprover.org/DSSynth/controller-synthesis-cav-2017.tar.gz}}
Our toolbox is available
online.\footnote{\url{https://github.com/ssvlab/dsverifier/tree/master/toolbox-dssynth}}

@@

The \tool performs the following automated steps
to synthesize a given digital controller:
%
\begin{enumerate}
%
\item \textbf{Setup}: obtains the physical plant, fixed-point format and
dynamic input ranges, and translates them to a specific structure in MATLAB.
%
\item \textbf{Parse}: obtains the digital system specification and translates 
it into an ANSI-C program.
%
\item \textbf{Execution}: obtains the ANSI-C program from the previous
(parse) step and calls our CEGIS engine as a back-end program synthesis tool
to perform the automated synthesis;
%
\item \textbf{Extraction}: obtains the ``.log'' file that is generated 
after the synthesis phase and then checks the synthesized digital-controller.
%
\item \textbf{Report}: obtains the digital controller from the previous
(extraction) step and translates it into MATLAB, for presentation to the
user.
%
\end{enumerate}

%---------------------------------------------------
\subsection{\tool Features}
%-----------------------------------------------

The features of the \tool can be summarized as follows:
%
\begin{itemize}
%
\item \textbf{Representation}: the synthesis can be 
performed for digital systems specified via 
transfer function or as state-space models.
%
\item \textbf{Fixed-Point Arithmetic}: the digital 
controller is synthesized considering FWL effects, 
using the given fixed-point numerical representation.
%
\item \textbf{Interface}: the synthesis can be executed via command-line or
graphical-user interface (GUI).  For the GUI application, the user can plot
the step response to reproduce the stability in closed-loop of the
synthesized digital controller.
%
\end{itemize}

@@

Users must provide a digital system described as a MATLAB model using a
\texttt{tf} (for transfer function) or an \texttt{ss} (for state-space
model) command (step $1$ of Fig.~\ref{fig:synthesis-flow}).  The \tool is
called via the command line in MATLAB as

@@

\noindent where \texttt{plant} is the physical plant in state-space or
transfer function representation, \texttt{intBits} is the integer part,
\texttt{fracBits} is the fractional part, \texttt{maxR} and \texttt{minR}
are the maximum and minimum dynamic range, respectively (steps $2$ and
$3$ of Fig.~\ref{fig:synthesis-flow}).
%
After executing the \texttt{synthesize} command, the \tool provides the
synthesized digital controller.

@@

To illustrate the usage of the \tool, Fig.~\ref{toolbox-usage} shows each
step of the synthesis process for a physical plant described in
Eq.~\eqref{equation_plant}, which represents a unmanned aerial vehicle
(UAV) quadcopter system~\cite{bouabdallah}.  This physical plant is
expressed by a transfer function $G(z)$, where $B(z)$ and $A(z)$ represent
the numerator and denominator, respectively, as
%
\begin{equation}
\label{equation_plant}
G(z)=\frac{B(z)}{A(z)}=\frac{-0.06875z^{2}}{z^2-1.696z+0.7089}.
\end{equation}

@@

In Fig.~\ref{toolbox-usage}, ``num'' represents $B(z)$ and ``den'' represent
$A(z)$, while $y$ represents the synthesized stable digital controller,
which is defined by Eq.~(\ref{equation_controller}).
%
\begin{equation}
\label{equation_controller}
C(z)=\frac{-0.9983^{2}+0.09587z+0.1926}{z^2+0.5665z+0.75}.
\end{equation}

>>>>

%---------------------------------------------------
\section{Synthesizing Digital Controllers with the \tool}
%---------------------------------------------------

@@

\begin{figure*}[t]
\centering
\includegraphics[width=0.7\textwidth]{synthesis-flow.pdf}
\caption{Phases of the Controller Synthesis}
\label{fig:synthesis-flow}
\end{figure*}

@@

In Step~1, the user selects the digital controller representation, which
can be a transfer function or a state-space model.  In Step~2, the
physical plant (in the form of Equation~(\ref{eq:transferfunction}) or
(\ref{eq:ss-example}), depending on representation) must be
given~\cite{astrom1997computer}.  Finally, in Step~3, the numerical
representation for the digital controller implementation must be set by the
user, i.e., the FWL format that defines the number of bits of the integer
and fractional parts as well as the dynamic range inputs.  The input 
provided by the user is a specification of the physical plant.

@@

Our CEGIS engine is implemented as an integrated module within the C bounded
model checker (CBMC)~\cite{cbmc}.  CBMC transforms the ANSI-C representation
of our closed-loop control system model into its internal format.  We
instrument this IR for each synthesis or verification scenario accordingly,
and use CBMC as an oracle to answer our queries.  CBMC itself relies on an
underlying SAT or SMT solver to solve verification conditions.  We~model FWL
effects, time discretization and the presence of quantization noise
explicitly using CBMC's nondeterminism API (e.g., \texttt{nondet},
\texttt{CPROVER\_assume} intrinsic functions).  Our module is included in
CBMC~5.8 and is available for
download.\footnote{\url{https://github.com/diffblue/cbmc/archive/cbmc-5.8.zip}}
We further created a VirtualBox OVA image with our tool pre-installed,
including our MATLAB-generated benchmarks and benchmark shell script with
instructions to run all benchmarks and reproduce our
experiments.\footnote{\url{www.cprover.org/DSSynth/controller-synthesis-cav-2017.tar.gz}}
Our toolbox is available
online.\footnote{\url{https://github.com/ssvlab/dsverifier/tree/master/toolbox-dssynth}}

@@

The \tool performs the following automated steps
to synthesize a digital controller for the given physical plant:
%
\begin{enumerate}
%
\item \textbf{Setup}: obtains the physical plant, fixed-point format and
dynamic input ranges, and translates them to a specific structure in MATLAB.
%
\item \textbf{Parse}: obtains the digital system specification and translates 
it into an ANSI-C program.
%
\item \textbf{Execution}: obtains the ANSI-C program from the previous
(parse) step and calls our CEGIS engine as a back-end program synthesis tool
to perform the automated synthesis.
%
\item \textbf{Extraction}: obtains the ``.log'' file that is generated 
after the synthesis phase and then checks the synthesized digital controller.
%
\item \textbf{Report}: obtains the digital controller from the previous
(extraction) step and translates it into MATLAB, for presentation to the
user.
%
\end{enumerate}

%---------------------------------------------------
%\subsection{\tool Features}
%-----------------------------------------------

%The features of the \tool can be summarized as follows:
%
%\begin{itemize}
%
%\item \textbf{Representation}: the synthesis can be 
%performed for digital systems specified via 
%transfer function or as state-space models.
%
%\item \textbf{Fixed-Point Arithmetic}: the digital 
%controller is synthesized considering FWL effects, 
%using the given fixed-point numerical representation.
%
%\item \textbf{Interface}: the synthesis can be executed via command-line or
%graphical-user interface (GUI).  For the GUI application, the user can plot
%the step response to reproduce the stability in closed-loop of the
%synthesized digital controller.
%
%\end{itemize}

@@

Users must provide a digital system described as a MATLAB model using a
\texttt{tf} (for transfer function) or an \texttt{ss} (for state-space
model) command (Step $1$ of Fig.~\ref{fig:synthesis-flow}).  The \tool is
called via the command line in MATLAB as

@@

\noindent where \texttt{plant} is the physical plant in state-space or
transfer function representation, \texttt{intBits} is the integer part,
\texttt{fracBits} is the fractional part, \texttt{maxR} and \texttt{minR}
are the maximum and minimum dynamic range, respectively (Steps $2$ and
$3$ of Fig.~\ref{fig:synthesis-flow}).
%
After executing the \texttt{synthesize} command, the \tool provides the
synthesized digital controller.

@@

Fig.~\ref{toolbox-usage} illustrates each
step of the synthesis process for a physical plant described in
Eq.~\eqref{equation_plant}, which represents an unmanned aerial vehicle
(UAV) quadcopter system~\cite{bouabdallah}.  This physical plant is
expressed by a transfer function $G(z)$, where $B(z)$ and $A(z)$ represent
the numerator and denominator, respectively, as
%
\begin{equation}
\label{equation_plant}
G(z)=\frac{B(z)}{A(z)}=\frac{-0.06875z^{2}}{z^2-1.696z+0.7089}.
\end{equation}

@@

In Fig.~\ref{toolbox-usage}, ``num'' represents $B(z)$ and ``den'' represents
$A(z)$, while $y$ represents the synthesized stable digital controller,
which is defined by Eq.~(\ref{equation_controller}).
%
\begin{equation}
\label{equation_controller}
C(z)=\frac{-0.9983^{2}+0.09587z+0.1926}{z^2+0.5665z+0.75}.
\end{equation}
